openarchaeoCollaboration

### 2021-02-27 analysis/paper.Rmd
Update plots for new GitHub data format

```{r plot-gh_lang}
oarch$gh_lang %>% 
  pivot_longer(everything(), names_to = "language", values_to = "n") %>% 
  drop_na(n) %>% 
  group_by(language) %>% 
  summarise(n = sum(n), .groups = "drop") %>% 
  arrange(-n) %>% 
  slice(1:10) %>% 
  ggplot(aes(fct_reorder(language, n, .desc = TRUE), n)) +
  geom_col() +
  labs(title = "Languages used in GitHub repositories",
       caption = "Data: <https://open-archaeo.info> and the GitHub API",
       x = "Language", y = "Bytes of code")
```

@@

```{r plot-gh_contributors-histogram}
oarch %>% 
  drop_na(gh_repo) %>% 
  unnest(gh_contributors) %>% 
  mutate(gh_repo = paste(gh_owner, gh_repo, sep = "/")) %>% 
  group_by(gh_repo) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  ggplot(aes(x = n)) +
  geom_histogram(binwidth = 1) +
  labs(
    title = "Repositories by number of contributors",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = "Contributors", y = "Repositories"
  )
```

>>>>

```{r plot-gh_langs, fig.show="hold", out.width="50%"}
oarch %>% 
  unnest(gh_langs) %>% 
  drop_na(lang, bytes) %>% 
  group_by(lang) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  arrange(-n) %>% 
  slice(1:10) %>% 
  ggplot(aes(fct_reorder(lang, n, .desc = TRUE), n)) +
  geom_col() +
  labs(title = "Languages used in GitHub repositories",
       subtitle = "Number of repositories using top 10 languages",
       caption = "Data: <https://open-archaeo.info> and the GitHub API",
       x = NULL, y = "Number of repositories")

oarch %>% 
  unnest(gh_langs) %>% 
  drop_na(lang, bytes) %>% 
  group_by(lang) %>% 
  summarise(bytes = sum(bytes), .groups = "drop") %>% 
  arrange(-bytes) %>% 
  slice(1:10) %>% 
  ggplot(aes(fct_reorder(lang, bytes, .desc = TRUE), bytes)) +
  geom_col() +
  labs(title = "Languages used in GitHub repositories",
       subtitle = "Total bytes of code in top 10 languages",
       caption = "Data: <https://open-archaeo.info> and the GitHub API",
       x = NULL, y = "Bytes")
```

@@

```{r plot-gh_contributors-histogram}
oarch %>% 
  drop_na(gh_repo) %>% 
  unnest(gh_contribs) %>% 
  group_by(gh_repo) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  ggplot(aes(x = n)) +
  geom_histogram(binwidth = 1) +
  labs(
    title = "Repository contributors",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = "Number of contributors", y = "Number of repositories"
  )
```
